Exception Handling Bug Hazards in Android

### 2015-10-08 SPRINGER_JOURNAL/msr_journal.tex
fixing refs
typo

The number of mobile apps is increasing in a daily rate. If on the one hand they
extend phones capabilities far beyond of the basic calls, on the other hand they have to 
cope with an increasing number of exceptinal conditions 
(e.g., faults in underlying middleware or hardware; compatibility issues~\cite{McDon13}; memory and battery restrictions; noisy external resources~\cite{Zhang12}).

@@

\begin{figure} \centering \includegraphics[scale=0.60]{charts/agree_new2.png}
\caption{How often developers throw and handle exceptions during app development.}
\label{fig:oftenhandle}
\end{figure}

>>>>

The number of mobile apps is increasing in a daily rate. If on the one hand they
extend phones capabilities far beyond of the basic calls, on the other hand they have to 
cope with an increasing number of exceptinal conditions 
(e.g., faults in underlying middleware or hardware; compatibility issues~\cite{McDon13}; memory and batery restrictions; noisy external resources~\cite{Zhang12}).

@@

\begin{figure} \centering \includegraphics[scale=0.58]{charts/agree_new2.png}
\caption{How often developers throw and handle exceptions during app development.}
\label{fig:oftenhandle}
\end{figure}
